---
title: "Homework 3"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r results='hide', message=FALSE}
library(tidyverse)
library(ggridges)
devtools::install_github("p8105/p8105.datasets")
library(p8105.datasets)
data("instacart")
```

The data 'instacart' contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. 
There are four character vairables: 'eval_set', 'product_name', 'aisle', and 'department'; and the other variables are all integer, such as 'order_id', 'order_number', 'order_dow'. Here listed few observations as example:
```{r echo=FALSE}
head(instacart, n = 3) %>% knitr::kable()
```

```{r}
aisle = 
  instacart %>% 
  select(aisle, aisle_id) %>% 
  group_by(aisle_id, aisle) %>% 
  count() %>% 
  arrange(desc(n))
head(aisle, n = 1) %>% knitr::kable(align = 'l')
```

There are `r nrow(aisle)` aisles, and most items are ordered from aisle number 83 "fresh vegetables".


```{r}
aisle %>% filter(n > 10000) %>% arrange(desc(n)) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.2) +
  labs(x = "Aisle Name", y = "Number Ordered") +
  scale_y_continuous(
    breaks  = c(20000, 40000,  60000,  80000,  100000, 120000, 140000, 160000)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 55, hjust = 1))
```

Among the aisle  “baking ingredients”, “dog food care”, and “packaged vegetables fruits”, the three most popular and their times of being ordered are shown in table below:

```{r}
popular_item =
  instacart %>% filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarise(order_times = n()) %>% 
  arrange(aisle, desc(order_times)) %>% 
  slice(1:3)

popular_item %>% knitr::kable(align = 'l')

```

The mean hour of the day at which "Pink Lady Apples" and "Coffee Ice Cream" are ordered on each day of the week are shown below:
```{r}
hour = 
  instacart %>% filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_hour"
  )

hour %>% knitr::kable(align = 'c', digits = 1)

```

## Problem 2

Load the data from package:
```{r}
data(brfss_smart2010)
brfss =
  brfss_smart2010 %>% janitor::clean_names() %>% 
  filter(
    topic == "Overall Health",
    response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")
    ) %>% 
  mutate(
    response = as.factor(response), 
    response = fct_relevel(response, c("Poor", "Fair", "Good", "Very good", "Excellent"))) %>% 
  arrange(response)

```

Find the states that were observed at 7 or more locations:
```{r}
#In 2002:
brfss %>% filter(year == "2002") %>% 
  group_by(locationabbr) %>% 
  summarise(number_observed = n_distinct(locationdesc))  %>% 
  filter(number_observed >= 7) %>% 
  knitr::kable()
```

In 2002, CT, FL, MA, NC, NJ and PA were observed at 7 or more locations;

```{r}
#In 2010:
brfss %>% filter(year == "2010") %>% 
  group_by(locationabbr) %>% 
  summarise(number_observed = n_distinct(locationdesc))  %>% 
  filter(number_observed >= 7) %>% 
  knitr::kable()
```

In 2010, CA, CO, FL, MA, MD, NC, NE, NJ, NY and OH were observed at 7 or more locations.



```{r}
#Construct a dataset that is limited to Excellent responses, and contains, year, state, and a variable that averages the data_value across locations within a state
average = 
  brfss %>% filter(response == "Excellent") %>% 
  group_by(year, locationabbr) %>% 
  summarise(avg_value = mean(data_value, na.rm = TRUE)) %>% 
  rename(state = locationabbr) 
#“Spaghetti” plot of this average value over time within a state
average %>%   
  ggplot(aes(x = year, y = avg_value)) +
  geom_line(aes(group = state)) +
  labs(y = "Average Data Value")
```

Two-panel plot showing distribution of data_value for responses (“Poor” to “Excellent”) among locations in NY State for the years 2006 and 2010 :
```{r}
#Filter NY state and year
ny_value = 
  brfss %>% filter(year %in% c("2006", "2010"), locationabbr == "NY") %>% 
  select(year, response, data_value)

#Make boxplot
ny_value %>% 
  ggplot(aes(x = response, y = data_value)) +
  geom_boxplot() +
  facet_grid(~year) +
  labs(y = "Data Value", x = "Response") 
```
Comparing the plots for 2006 and 2010, we can see that the median data value in each response group did not change much except the small elevation in the 'very good' group.

## Problem 3

