---
title: "Homework 3"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Problem 1

```{r results='hide', message=FALSE}
library(tidyverse)
library(ggridges)
library(p8105.datasets)
data("instacart")
```

The data 'instacart' contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. 
There are four character vairables: 'eval_set', 'product_name', 'aisle', and 'department'; and the other variables are all integer, such as 'order_id', 'order_number', 'order_dow'. Here listed few observations as example:
```{r echo=FALSE}
head(instacart, n = 3) %>% knitr::kable()
```

```{r}
aisle = 
  instacart %>% 
  select(aisle, aisle_id) %>% 
  group_by(aisle_id, aisle) %>% 
  count() %>% 
  arrange(desc(n))
head(aisle, n = 1) %>% knitr::kable(align = 'l')
```

There are `r nrow(aisle)` aisles, and most items are ordered from aisle number 83 "fresh vegetables".


```{r}
aisle %>% filter(n > 10000) %>% arrange(desc(n)) %>% 
  ggplot(aes(x = aisle, y = n)) +
  geom_bar(stat = "identity", fill = "steelblue", width = 0.2) +
  labs(x = "Aisle Name", y = "Number Ordered") +
  scale_y_continuous(
    breaks  = c(20000, 40000,  60000,  80000,  100000, 120000, 140000, 160000)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 55, hjust = 1))
```

Among the aisle  “baking ingredients”, “dog food care”, and “packaged vegetables fruits”, the three most popular and their times of being ordered are shown in table below:

```{r}
popular_item =
  instacart %>% filter(aisle %in% c("baking ingredients", "dog food care", "packaged vegetables fruits")) %>% 
  group_by(aisle, product_name) %>% 
  summarise(order_times = n()) %>% 
  arrange(aisle, desc(order_times)) %>% 
  slice(1:3)

popular_item %>% knitr::kable(align = 'l')

```

The mean hour of the day at which "Pink Lady Apples" and "Coffee Ice Cream" are ordered on each day of the week are shown below:
```{r}
hour = 
  instacart %>% filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  select(product_name, order_dow, order_hour_of_day) %>% 
  group_by(product_name, order_dow) %>% 
  summarise(mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    names_from = "order_dow",
    values_from = "mean_hour"
  )

hour %>% knitr::kable(align = 'c', digits = 1)

```




